Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-04-19 0.abstract.tex
middle coss

Three dimensional electron microscopy is becoming a very data-intensive field in which vast amounts of experimental images are acquired at high speed. To manage such large-scale projects, we had previously developed  a modular workflow system called \scipion \citep{delarosatrevin2016}. We present here a major extension of \scipion that allows stream processing of EM images while the data is being acquired. This approach helps to detect problems at early stages, saves computing time and provides users with a detailed evaluation of the data quality before the acquisition is finished. Different EM facilities have 
implemented their stream processing solution using custom-made scripts, but this script based approach is not flexible and present a slow response time to new feature requests. The advantages of our proposed solution are: (1) flexibility: users can customize their workflows from a  large collection of preloaded algorithms; (2) repeatability and traceability: workflows are stored and can be re-executed later, either with the same data or with a different data set; (3) monitorization: there are utilities that constantly check how the execution of the algorithms is going on and inform about possible anomalies; (4) reports: we have developed several graphical interfaces that are updated periodically producing a summary (e.g, CTF defocus values, system load, etc). This summary may be generated in HTML format and  published though a public web-site to provide access for external users; (5) backup: both local and remote backup of the data and image processing is provided. At present, \scipion has been installed and is in production mode in seven Cryo-EM facilities and it is being considered in many more.

\textbf{Keywords:} electron microscopy, streaming, image processing, live processing, high throughput

>>>>

Three dimensional electron microscopy is becoming a very data-intensive field in which vast amounts of experimental images are acquired at high speed. To manage such large-scale projects, we had previously developed  a modular workflow system called \scipion \citep{delarosatrevin2016}. We present here a major extension of \scipion that allows stream processing of EM images while the data is being acquired. This approach helps to detect problems at early stages, saves computing time and provides users with a detailed evaluation of the data quality before the acquisition is finished. Different EM facilities have 
implemented their stream processing solution using custom-made scripts, but this script based approach is not flexible and present a slow response time to new feature requests. The advantages of our proposed solution are: (1) flexibility: users can customize their workflows from a  large collection of preloaded algorithms; (2) repeatability and traceability: workflows are stored and can be re-executed later, either with the same data or with a different data set; (3) monitorization: there are utilities that constantly check how the execution of the algorithms is going on and inform about possible anomalies; (4) reports: we have developed several graphical interfaces that are updated periodically producing a summary (e.g, CTF defocus values, system load, etc). This summary may be generated in HTML format and  published through a public web-site to provide access for external users; (5) backup: both local and remote backup of the data and image processing is provided. At present, \scipion has been installed and is in production mode in seven Cryo-EM facilities throughout the world and, it is being considered in many more.

\textbf{Keywords:} electron microscopy, streaming, image processing, live processing, high throughput, Scipion

### 2018-04-19 1.introduction.tex
middle coss

For most cases, the future of projects that require high-end microscopes is through centralized microscopy facilities, in which automatic acquired data needs to be monitored by users and facility staff.  With this scenario in mind, we have redesigned \scipion which is a software framework for integrating several 3DEM software packages through a workflow-based approach \citep{delarosatrevin2016}. % in which the early detection of issues may save a data acquisition shift which otherwise needs to be repeated after a new application that may be granted many months later. 
In this way, \scipion starts the processing of the movies as they are being acquired with the double aim of checking for possible data collection errors and execute a first user-tailored image processing workflow that provides users with an accurate estimation of the acquired data quality.

Many software packages have been developed to provide automated data collection, such as SerialEM \citep{Mastronarde2005}, Leginon \citep{Suloway2009}, UCSF-Tomography \citep{Zheng2007}, Tom Toolbox \citep{Nickell2005}, EPU \citep{EPU}, Latitude in Digital Micrograph \citep{Latitude}, EMMenu \citep{emmenu}, etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well addressed. In fact, in most places this is accomplished through home made scripts \citep[i.e.][]{Pichkur2018}. %(i.e. \citet{Pichkur2018}).
Exceptions are UCSFImage4 \citep{Li2015} and Focus \citep{Biyani2017}. As we will show in this article, \scipion differs from these solutions in a larger flexibility, both from the point of view of users and facility staff.

>>>>

For most cases, the future of projects that require high-end microscopes is through centralized microscopy facilities, in which automatically acquired data needs to be monitored by users and facility staff.  With this scenario in mind, we have redesigned \scipion which is a software framework for integrating several 3DEM software packages through a workflow-based approach \citep{delarosatrevin2016}. % in which the early detection of issues may save a data acquisition shift which otherwise needs to be repeated after a new application that may be granted many months later. 
In this way, \scipion starts the processing of the movies as they are being acquired with the double aim of checking for possible data collection errors and execute a first user-tailored image processing workflow that provides users with an accurate estimation of the acquired data quality.

Many software packages have been developed to provide automated data collection, such as SerialEM \citep{Mastronarde2005}, Leginon \citep{Suloway2009}, UCSF-Tomography \citep{Zheng2007}, Tom Toolbox \citep{Nickell2005}, EPU \citep{EPU}, Latitude in Digital Micrograph \citep{Latitude}, EMMenu \citep{emmenu}, etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well addressed. In fact, in most places this is accomplished through home made scripts \citep[e.g.][]{Pichkur2018}. %(i.e. \citet{Pichkur2018}).
Exceptions are UCSFImage4 \citep{Li2015}, Focus \citep{Biyani2017} and Relion \citep{fernandez2017:relion-pipeline}. As we will show in this article, \scipion differs from these solutions in a larger flexibility, both from the point of view of users and facility staff.

### 2018-04-19 2.overall.tex
middle coss

\subsection{Stream Processing}
The main change introduced in \scipion is \emph{stream processing}, that is, computing on data directly as it is produced or received.
In this way, a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion version 1.2, users may find  the first steps in the image processing workflow adapted to streaming, including movie alignment,  CTF estimation and particle picking and extraction. In the developers version, several 2D classification algorithms are being adapted for this new way of processing.

@@

We would like to finish this section stressing that despite the modifications introduced to \scipion data and process model, the framework keeps providing full data provenance. That is, \scipion provides detailed information about the origin of the data  and the process to generate it.

@@

\scipion is a flexible framework that allows to create different workflows by choosing among many algorithms at each step. In this work we do not recommend a particular workflow  over others since we realize that different specimens, microscopes or facilities may have different requirements. Nevertheless, since a use case may clarify \scipion capabilities, in the following we describe the pipeline offered by default at the \emph{Centro Nacional de Biotecnolog\'{i}a} (CNB) cryoEM Facility.

The workflow starts two independent protocols in parallel. The first protocol estimates the camera gain at each pixel for a few  movies \citep{sorzano2018}. % In the CNB setup the microscope camera is calibrated and internally performs the gain correction before writing the movies so the estimated gain image should be almost constant and equal to 1. 
The output of this protocol serves as verification of the validity of the experimental gain image for the whole data set. The second protocol performs direct detector movie alignment. Currently \scipion offers  five  methods for movie alignment: motioncorr \cite{Li2015}, motioncor2 \citep{Zheng2016:motioncor2}, correlation (an unpublished CPU version that implements the global alignment method used by motioncor \citep{Li2013:motioncorr}), unblur \citep{Grant2015:unblur} and optical flow \citep{Abrishami2015:optical-flow}. Then the CTF of the resulting micrographs are calculated. Scipion provides three CTF estimation methods:
CTFFIND4 (Rohou and Grigorieff, 2015), gCTF (Zhang, 2016) and Xmipp CTF estimation (Sorzano et al., 2007; Vargas et al., 2013). At this point the user may compute the CTFs using several algorithms and compare them with the protocol \protocol{CTF consensus} that reports up to which frequency two estimation of the same micrograph are equivalent. Further automatic filtering based on CTF is available through the protocol \protocol{CTF filtering} that selects micrographs based on the astigmatism, resolution and defocus. %Another criteria for CTF selection is iciness, that is,  the ratio of the intensity in the resolution band between 3.5 and 3.9 \AA, and between 6 and 30 \AA, which gives a good estimate of the ice crystal content of the vitreous specimen.

@@

Two new streaming protocols are under development and will join the described  pipeline in a near future. The first one will perform 2D classification and the second one will create a initial 3D map based on this classes. A first version of these protocols is available in the \scipion developers version.

As commented in section \ref{overall}, to monitor, chart and create alerts  we have developed a set of metaprotocols. By default \protocol{system}, \protocol{CTF} and \protocol{report monitors} are executed. \protocol{System monitor} reports on  CPU and GPU usage, memory consumption and, disk I/O. \protocol{CTF monitor} plots the CTF defocus and astigmatism  and it will raise an alarm if these parameters are not within a given range. Finally the \protocol{report} protocol pushes all the created plots and summaries to a web server so this information can be accessed by users who are not physically in the microscope room.

>>>>

\subsection{Stream Processing}
The main change introduced in \scipion is \emph{stream processing}, that is, computing on data directly as they are produced or received.
In this way, a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion version 1.2, users may find  the first steps in the image processing workflow adapted to streaming, including movie alignment,  CTF estimation and particle picking and extraction. In the developers version, several 2D classification algorithms are being adapted for this new way of processing.

@@

We would like to finish this section stressing that despite the modifications introduced to \scipion data and process model, the framework keeps providing full data provenance and backward compatibility. That is, \scipion provides detailed information about the origin of the data  and the process to generate it.

@@

\scipion is a flexible framework that allows to create different workflows by choosing among many algorithms at each step. In this work we do not recommend a particular workflow  over others since we realize that different specimens, microscopes or facilities may have different requirements. Nevertheless, since a use case may clarify \scipion capabilities, in the following we describe the pipeline offered by default at the \emph{National Center for Biotechnology} (CNB) cryoEM Facility.

The workflow starts two independent protocols in parallel. The first protocol estimates the camera gain at each pixel for a few  movies \citep{sorzano2018}. % In the CNB setup the microscope camera is calibrated and internally performs the gain correction before writing the movies so the estimated gain image should be almost constant and equal to 1. 
The output of this protocol serves as verification of the validity of the experimental gain image for the whole data set. The second protocol performs direct detector movie alignment. Currently \scipion offers  five  methods for movie alignment: motioncorr \citep{Li2015}, motioncor2 \citep{Zheng2016:motioncor2}, correlation (an unpublished CPU version that implements in Xmipp a global alignment method and solves it similarly to motioncorr but using robust statistics), unblur \citep{Grant2015:unblur} and optical flow \citep{Abrishami2015:optical-flow}. Then the CTF of the resulting micrographs are calculated. Scipion provides three CTF estimation methods:
CTFFIND4 (Rohou and Grigorieff, 2015), gCTF (Zhang, 2016) and Xmipp CTF estimation (Sorzano et al., 2007; Vargas et al., 2013). At this point the user may compute the CTFs using several algorithms and compare them with the protocol \protocol{CTF consensus} that reports up to which frequency two estimation of the same micrograph are equivalent. Further automatic filtering based on CTF is available through the protocol \protocol{CTF filtering} that selects micrographs based on the astigmatism, resolution and defocus. %Another criteria for CTF selection is iciness, that is,  the ratio of the intensity in the resolution band between 3.5 and 3.9 \AA, and between 6 and 30 \AA, which gives a good estimate of the ice crystal content of the vitreous specimen.

@@

Two new streaming protocols are under development and will join the described  pipeline in a near future. The first one will perform 2D classification and the second one will create a initial 3D map based on these classes. A first version of these protocols is available in the \scipion developers version.

As commented in Section \ref{overall}, to monitor, chart and create alerts  we have developed a set of metaprotocols. By default, \protocol{system}, \protocol{CTF} and \protocol{report monitors} are executed. \protocol{System monitor} reports on  CPU and GPU usage, memory consumption, and disk I/O. \protocol{CTF monitor} plots the CTF defocus and astigmatism  and it will raise an alarm if these parameters are not within a given range. Finally the \protocol{report} protocol pushes all the created plots and summaries to a web server so this information can be accessed by users who are not physically in the microscope room.

### 2018-04-19 3.workflow_cnb.tex
middle coss

\subsection{Case 1: Scipion at CNB}
The National Center for Biotechnology (CNB) forms part of the Spanish National Research Council (CSIC), the largest public research institution in Spain. 
The CNB Cryo-Electron Microscopy Facility is a joint effort of the Centro Nacional de Biotecnolog\'{i}a (CNB-CSIC) and the Centro de Investigaciones Biol\'{o}gicas (CIB-CSIC). The mission of the facility is to provide researchers access to the latest cryo-EM technology for high resolution imaging.

@@

At the beginning CNB networking setup was a quite straight forward one, movies where stored in the  same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in lineal mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

@@

Data sets are recorded using \epu. The microscope control system has a 70 TB NAS (Network-attached storage) unit for saving movies as they are obtained (we will refer to this NAS as microscope-NAS). This storage unit is shared through a Samba share and connected to the private network using a 10Gb connexion. \scipion is executed on a Linux server which has two 1Gb NICs (network interface controllers) that connect it to the private and the LAN networks respectively (we will refer to this machine as \scipionbox). \scipionbox has 32 CPUs at 2.40GHz, 62 Gb of RAM memory and 2 \textit{Quadro M4000} GPUs. Finally, a second NAS with 4 1Gb NICs is linked to the private, LAN and WAN networks (we will refer to this second NAS as output-NAS).

The data flow is a follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox will temporary read the movies from 
the microscope-NAS but will not store them locally, (c) each hour, output-NAS will connect to \scipionbox and copy -or update- the last \scipion project, (d) at the same time output-NAS may be either executing a script to incrementally backup \scipion project and the movies to a USB disk or serve this information through the Internet and, (e) in parallel, \scipionbox transfers to  output-NAS different html reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox}).

Although CNB staff try to discourage the use of external USB hard disks versus network as way of retrieving the raw and processed data, this is the preferred option for most users.
USB 3.0 drives can theoretically handle data flows of 300 MB/s, but CNB experience is that, in this busy environment, many of them  have trouble exceeding 50 MB/s. In most cases, 50 MB/s is enough to transfer the data before the following microscope shift starts. Nevertheless, real-world is tough and it happens that two, or even three,  users try to download their data simultaneously. Fortunately, output-NAS works as front-end and isolates the data acquiring and processing infrastructure from the user downloading. Network users access to output-NAS using a chrooted common account. This account only allows rsync connections and make impossible to retrieve data if the name of the project to be downloaded is unknown. In order to speed up transfer weak ciphers (as \emph{arcfour}) has been activated in output-NAS.

@@

\begin{enumerate}
 \item Transparent addition of new workflows. \scipion is able to export any executed workflow as a json file. \emadmin can import this files and use them to create new predetermined workflows.
 \item Automatic creation of pdf user's report containing: microscope acquisition parameters and histograms summarizing data resolution and  defocus. 
 \item The above mentioned information is stored in a database for further analysis. By default the system plots the  average resolution and astigmatism of the different acquisitions versus time
 \item Remote management. \emadmin is a client server application, the client maybe executed in a machine different from the one that executes \scipion
 \item Automatic backup of the \scipion project
 \item \scipion is able to create live html reports on the image acquisition process. \emadmin keeps track of all of them and facilitates the access to this information
\end{enumerate}

>>>>

\subsection{Case 1: Scipion at CNB}
The National Center for Biotechnology (CNB) forms part of the Spanish National Research Council (CSIC), the largest public research institution in Spain. 
The CNB Cryo-Electron Microscopy Facility is a joint effort of the Nacional Center for Biotechnology (CNB-CSIC) and the Biological Research Centers (CIB-CSIC). The mission of the facility is to provide researchers access to the latest cryo-EM technology for high resolution imaging.

@@

At the beginning CNB networking setup was a quite straightforward one, movies where stored in the  same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in lineal mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

@@

Data sets are recorded using \epu. The microscope control system has a 70 TB NAS (Network-attached storage) unit for saving movies as they are obtained (we will refer to this NAS as microscope-NAS). This storage unit is shared through a Samba share and connected to the private network using a 10Gb connexion. \scipion is executed on a Linux server which has two 1Gb NICs (network interface controllers) that connect it to the private and the LAN networks respectively (we will refer to this machine as \scipionbox). \scipionbox has 32 CPUs at 2.40GHz, 62 Gb of RAM memory and 2 \textit{Quadro M4000} GPUs. Finally, a second NAS with four 1Gb NICs is linked to the private, LAN and WAN networks (we will refer to this second NAS as output-NAS).

The data flow is a follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox will temporary read the movies from 
the microscope-NAS but will not store them locally, (c) each hour, output-NAS will connect to \scipionbox and copy -or update- the last \scipion project, (d) at the same time output-NAS may be either executing a script to incrementally backup \scipion project and the movies to a USB disk or serve this information through the Internet and, (e) in parallel, \scipionbox transfers to  output-NAS different HTML reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox}).

Although CNB staff try to discourage the use of external USB hard disks versus network as way of retrieving the raw and processed data, this is the preferred option for most users.
USB 3.0 drives can theoretically handle data flows of 300 MB/s, but CNB experience is that, in this busy environment, many of them  have trouble exceeding 50 MB/s. In most cases, 50 MB/s is enough to transfer the data before the following microscope shift starts. Nevertheless, real-world is tough and it happens that two, or even three,  users try to download their data simultaneously. Fortunately, output-NAS works as front-end and isolates the data acquiring and processing infrastructure from the user downloading. Network users access to output-NAS using a chrooted common account. This account only allows rsync connections and make impossible to retrieve data if the name of the project to be downloaded is unknown. In order to speed up transfer, weak ciphers (as \emph{arcfour}) has been activated in output-NAS.

@@

\begin{enumerate}
 \item Transparent addition of new workflows. \scipion is able to export any executed workflow as a json file. \emadmin can import this files and use them to create new predetermined workflows.
 \item Automatic creation of pdf user's report containing: microscope acquisition parameters and histograms summarizing data resolution and  defocus. 
 \item The above mentioned information is stored in a database for further analysis. By default the system plots the  average resolution and astigmatism of the different acquisitions versus time.
 \item Remote management. \emadmin is a client server application, the client maybe executed in a machine different from the one that executes \scipion.
 \item Automatic backup of the \scipion project.
 \item \scipion is able to create live HTML reports on the image acquisition process. \emadmin keeps track of all of them and facilitates the access to this information.
\end{enumerate}

### 2018-04-19 3.workflow_diamond.tex
middle coss

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system has been developed which allocates each user with a unique federal identity (IDs), and associates those user IDs with the experiments in which they partake in. Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{Delageniere2011:ispb},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting  %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X

>>>>

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system has been developed which allocates each user with a unique federal identity (IDs), and associates those user IDs with the experiments in which they partake in. Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{Delageniere2011:ispb},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting. %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X

### 2018-04-19 scipionbox.tex
Stefan
middle coss

\begin{document}
\title{Using Scipion for Stream Image Processing at Electron Microscopy Facilities}
Authors to be sorted later
\author{C.O.S. Sorzano$^{(a)}$,
A. Jim\'{e}nez$^{(a)}$,
R. Melero$^{(a)}$,\\
M. Mart\'{i}nez$^{(a)}$,
J. G\'{o}mez-Blanco$^{(a)}$,
L. del Cano$^{(a)}$,\\
T. Majtner$^{(a)}$,
E. Ram\'{i}rez$^{(a)}$,
P. Conesa$^{(a)}$,\\
J.L. Vilas$^{(a)}$,
R. Marabini$^{(a)}$,
Y. Rancel$^{(a)}$,
J.M. Carazo$^{(a)}$,\\
J.M. de la Rosa-Trev\'{i}n$^{(c)}$,
M. Carroni$^{(c)}$,
S. Fleichman $^{(c)}$,\\
E. Lindahl$^{(c,d)}$
A.W. Ashton$^{(e)}$,
M. Basham$^{(e)}$,\\
D.K. Clare$^{(e)}$,
K. Savage$^{(e)}$,
C.A. Siebert$^{(e)}$,\\
D. Maluenda$^{(a)}$
        }

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(c)}$ Department of Biochemistry and Biophysics, Science for Life Laboratory, Stockholm University, Stockholm, Sweden}} 
\lyxaddress{{\small$^{(d)}$ Swedish e-Science Research Center, KTH Royal Institute of Technology, Stockholm, Sweden}}
\lyxaddress{{\small$^{(e)}$ Diamond Light Source, Harwell Science and Innovation Campus, Didcot OX11 0DE, England}}
%This document provides a preliminary analysis of the data collected by the CTF Challenge (http://i2pc.cnb.csic.es/3dembenchmark/LoadHome.htm). Figures/tables/plots/etc are located at the document's end. 
\setcounter{figure}{2}%I do not know why but figure counter starts with -1
\textbf{Corresponding Author: Roberto Marabini, Ph = +34 91 5854510, email: roberto@cnb.csic.es\\} %Roberto Marabini, Ph= 34 91 5854510, email: roberto@cnb.csic.es\\
%Escuela Polit\'{e}cnica Superior\\
%Universidad Aut\'{o}noma de Madrid\\
%28049 Cantoblanco\\
%Madrid\\
%Spain

>>>>

\begin{document}
\title{Using Scipion for Stream Image Processing at Cryo-EM Facilities}
Authors to be sorted later
\author{C.O.S. Sorzano$^{(b)}$,
A. Jim\'{e}nez$^{(b)}$,
R. Melero$^{(b)}$,\\
M. Mart\'{i}nez$^{(b)}$,
J. G\'{o}mez-Blanco$^{(b)}$,
L. del Cano$^{(b)}$,\\
T. Majtner$^{(b)}$,
E. Ram\'{i}rez$^{(b)}$,
P. Conesa$^{(b)}$,\\
J.L. Vilas$^{(b)}$,
R. Marabini$^{(a)}$,
Y. Rancel$^{(b)}$,
J.M. Carazo$^{(b)}$,\\
J.M. de la Rosa-Trev\'{i}n$^{(c)}$,
M. Carroni$^{(c)}$,
S. Fleischmann $^{(c)}$,\\
E. Lindahl$^{(c,d)}$
A.W. Ashton$^{(e)}$,
M. Basham$^{(e)}$,\\
D.K. Clare$^{(e)}$,
K. Savage$^{(e)}$,
C.A. Siebert$^{(e)}$,\\
D. Maluenda$^{(a)}$,\\
Grigory G. Sharov$^{(f)}$
        }

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(c)}$ Department of Biochemistry and Biophysics, Science for Life Laboratory, Stockholm University, Stockholm, Sweden}} 
\lyxaddress{{\small$^{(d)}$ Swedish e-Science Research Center, KTH Royal Institute of Technology, Stockholm, Sweden}}
\lyxaddress{{\small$^{(e)}$ Diamond Light Source, Harwell Science and Innovation Campus, Didcot OX11 0DE, United Kingdom}}
\lyxaddress{{\small$^{(f)}$ MRC Laboratory of Molecular Biology - Structural studies, Cambridge, England, United Kingdom}}

%This document provides a preliminary analysis of the data collected by the CTF Challenge (http://i2pc.cnb.csic.es/3dembenchmark/LoadHome.htm). Figures/tables/plots/etc are located at the document's end. 
\setcounter{figure}{2}%I do not know why but figure counter starts with -1
\textbf{Corresponding Author: Roberto Marabini, Ph = +34 91 5854510, email: roberto@cnb.csic.es\\} %Roberto Marabini, Ph= 34 91 5854510, email: roberto@cnb.csic.es\\
%Escuela Polit\'{e}cnica Superior\\
%Universidad Aut\'{o}noma de Madrid\\
%28049 Cantoblanco\\
%Madrid\\
%Spain
